Characterization of gaps in directly bonded Si compound optics

### 2014-03-20 AO_bondedSi.tex
some tweaks

\section{Measurement strategy, conditions, and details}
The measurements were performed with an Agilent Cary 5000 UV-Vis-NIR spectrophotometer \cite{cary5000web}.  The typical measurement parameters and tool performance are listed below.  More details about the tool are available at the vendor's website.  Briefly, the tool has a double monochromator.  The double monochromator feature reduces scattered light.  The vendor reported linearity exceeding 40 dB.

The Cary 5000 has four operation modes: single front, single back, double, and double reverse.  We experimented with single front and double modes.  Double mode takes a reference spectrum simultaneously to the target spectrum.  In both single and double beam mode a baseline scan is taken of air.  The baseline spectrum is the raw spectral response of the system, which is automatically divided out of subsequent spectra.  In single beam mode the baseline measurements must be repeated about every half hour.  We estimated the uncertainty and measurement repeatability of single and double modes in the following way.  We computed the RMS error and measurement repeatability in a single measurement by computing the standard deviation of the beam with no sample in a series of spectra taken immediately after a 100\% baseline scan.  The predicted mean level should naturally be 100\%.  We found that the mean value in single mode drifted by about 0.2\%.  The standard deviation of the featureless spectrum was typically 0.02\%, with some portions of the spectrum demonstrating increased uncertainty, perhaps attributable to atmospheric absorption. In double beam mode the spectrograph performance was much better.  We put a double side polished Si wafer in the reference beam, and no sample in the target beam during the baseline scan.  In this way the transmission spectrum of a target Si wafer is automatically normalized.  The double beam mode effectively divides out variations in the mean transmission levels attributable to lamp drift at 0.2\% in single beam measurements.  The drift in mean transmission level is merely 0.02\% in double beam mode.  These values are accurate for measurements over a half hour timescale or less.  Over periods of hours the drift increases for both single and double beam mode, so a repeat baseline scan is sometimes necessary.  The need for repeat baselines is more acute for single mode.

>>>>

\section{Measurement strategy, conditions, and details}
The measurements were performed with an Agilent Cary 5000 UV-Vis-NIR spectrophotometer \cite{cary5000web}.  The typical measurement parameters and tool performance are listed below.  More details about the tool are available at the vendor's website.  Briefly, the tool has a double monochromator.  The double monochromator feature reduces scattered light.  The vendor reported linearity exceeds 40 dB.

The Cary 5000 has four operation modes: single front, single back, double, and double reverse.  We experimented with single front and double modes.  Double mode takes a reference spectrum simultaneously to the target spectrum.  In both single and double beam mode a baseline scan is taken of air.  The baseline spectrum is the raw spectral response of the system, which is automatically divided out of subsequent spectra.  In single beam mode the baseline measurements must be repeated about every half hour.  We estimated the uncertainty and measurement repeatability of single and double modes in the following way.  We computed the RMS error and measurement repeatability in a single measurement by computing the standard deviation of the beam with no sample in a series of spectra taken immediately after a 100\% baseline scan.  The predicted mean level should naturally be 100\%.  We found that the mean value in single mode drifted by about 0.2\%.  The standard deviation of the featureless spectrum was typically 0.02\%, with some portions of the spectrum demonstrating increased variance, perhaps attributable to atmospheric absorption. In double beam mode the spectrograph performance was much better.  We put a double side polished Si wafer in the reference beam, and no sample in the target beam during the baseline scan.  In this way the transmission spectrum of a target Si wafer is automatically normalized.  The double beam mode effectively divides out the 0.2\% drift in the mean transmission level attributable to lamp drift, as seen in single beam measurements.  In double beam mode, the drift in mean transmission level is merely 0.02\%.  These values are accurate for measurements over a half hour timescale or less.  Over periods of hours the drift increases for both single and double beam mode, so a repeat baseline scan is sometimes necessary.  The need for repeat baselines is more acute for single mode.
